Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-09 paper/v2/paper-edited.tex
update failure analysis section + code

\newcommand{\CD}[1]{\texttt{\small #1}}  % code font
\newcommand{\KW}[1]{\texttt{\small\bfseries{#1}}}
%\newcommand{\KW}[1]{\texttt{#1}}
\newcommand{\True}{\CD{true}}
\newcommand{\Define}{\KW{define}}
\newcommand{\Prefer}{\texttt{>>}}
\newcommand{\Path}{\texttt{=>}}
\newcommand{\Link}{\texttt{->}}
\newcommand{\Agg}{\KW{agg}}
\newcommand{\Any}{\KW{any}}
\newcommand{\None}{\KW{none}}
\newcommand{\In}{\KW{in}}
\newcommand{\Out}{\KW{out}}
\newcommand{\AND}{\texttt{\&}}
\newcommand{\OR}{\texttt{|}}
\newcommand{\NOT}{\texttt{!}}
\newcommand{\Intersect}{\ensuremath{\cap}}
\newcommand{\Union}{\ensuremath{\cup}}

@@

Once \sysname compiles the policy, it is guaranteed to be compliant under all possible failure scenarios, modulo aggregation black holes (which are unavoidable in general). In the presence of aggregation, the \sysname compiler will also efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.

@@

%Regular expressions are an expressive formalism that have been used extensively for describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}. Our regular expression language differs from others by allowing operators to describe preferences between paths.

@@

  \caption{Regular Intermediate Language (RIL) syntax (left), and
           Propane language expansions (right).}
  \label{fig:rir-syntax}
  \vspace{-1em}
\end{figure*}

@@

The main differences between the FE and RIR are: $i)$ FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, $ii)$ FE provides high-level names that abstract sets of routes and groups of prefixes/neighbors, and $iii)$ FE allows the preference operator to be used more flexibly.

A key constraint when translating FE to RIR is to ensure that all specified routes are well-formed. In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$. This ensures that the user only control traffic that goes through the user's network at some point, and that such traffic does not loop back multiple times to the user network.

The translation from \sysname to RIR is based on a set of rewriting rules.
The first step merges separate constraints. It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by ($\Any \cap \NOT(a)$), where $\Any$ ensures the routes are well-formed.
%
For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:

@@

The next step rewrites the high-level constraints such as \textit{enter} according to the equivalences in Figure~\ref{fig:rir-syntax}. Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression. For example, the regular expression $a \cdot (b \Prefer c) \cdot d$ is lifted to $(a \cdot b \cdot d) \Prefer (a \cdot c \cdot d)$ by distributing the preference over the sequence operator. In general, we employ the follwing distributivity equivalences:
%
\[ 
\begin{array}{c}
  x \odot (y_1 \Prefer \dots \Prefer y_n) = (x \odot y_1) \Prefer \dots \Prefer (x \odot y_n) \\
  (y_1 \Prefer \dots \Prefer y_n) \odot x = (y_1 \odot x) \Prefer \dots \Prefer (y_n \odot x)
\end{array}
\]
%
where $\odot$ stands for an arbitrary regular binary operator. Preferences nested under a unary operator, \textit{star} or \textit{negation}, are flagged by the compiler as invalid policies.

@@

  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
  \label{fig:example-compilation}
  \vspace{-1em}
\end{figure*}

Now that the user policy exists in a simplified form, we must consider topology. In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints. Our PGIR captures these dependencies by ``intersecting" each of the regular automata corresponding to the RIR path preferences, and the topology. Paths through the PGIR correspond to real paths through the topology that satisfy the user constraints.

@@

% Formally define automata
The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$. While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., route announcements flowing in the opposite direction). To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression. Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ consists of all all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
% Formally define topology
The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
%
% Formally define product graph
The combined PGIR is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon 2^{V' \times V'}$,
a unique starting vertex $s$,
a unique ending vertex $e$,
and a preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. 
Two nodes $x$ and $y$ \emph{shadow} each other in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$. That is, $x$ and $y$ shadow each other when they are different nodes in the PGIR that represent the same topology location.

@@

Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between routers.
%
Consider the topology in Figure~\ref{fig:example-compilation}. Suppose we want a primary route from W that enters the network from $A$, and utilizes the A--C and C--D links. We also want a backup route that enters from $B$, and utilizes the B--C link, but is otherwise unconstrained. For simplicity, we assume that the route can end in either $X$, $Y$, or $Z$. The RIR for the policy is:
%
$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$$
%
Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
%
The figure also shows the PGIR after intersecting the topology and policy automata. Every path in it corresponds to a concrete path in the topology. In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
%
For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining the most prefered preference $1$.
BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This is reflected in the product graph by the node with state $(X,1,1)$. From here, if X were to advertise this route to D, it would result in the path $D \cdot X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
%
The ``--" state indicates the corresponding automaton can not accept the current path or any extension of it. Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.

@@

Before checking if policies captured by the PGIR are safe, we minimize the PGIR to improve our safety analysis. 
The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops. In particular, BGP's loop prevention mechanism forces an AS to reject any route for which it is already in the AS path.
%
For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 1 policy, but which contains a loop.
%
It often improves the precision of the failure-safety analysis to eliminate cases that are not possible due to loops. 
%For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node.
%We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
%
%Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.

@@

To implement path preferences in routing, BGP uses local preferences on a per-device basis. However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult, particularly in the presence of failures. For example, imagine an extremely simple policy for the topology in Figure~\ref{fig:example-compilation}, which says to prefer one route over another:
%
$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D}) \Prefer (\CD{W} \cdot \CD{B} \cdot \CD{C} \cdot \CD{E})$.
%

How could such a policy be implemented in BGP? Suppose we set the local preference at router $C$ to prefer $D$ over $E$, and use the BGP MED attribute to influence $W$ to prefer $A$ over $B$. This might work as expected under normal conditions, however, if the A -- C link fails, then suddenly $C$ has made the wrong decision. Traffic will now follow the
$W \cdot B \cdot C \cdot D$ path, even though this path was not specified by the policy. This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy. To make matters worse, the second preference $W \cdot B \cdot C \cdot E$ is available in the network but not being used. This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
We could solve the first problem by filtering routes that go through $D$ at $B$, however, we can not fix the second problem---$C$ has made the wrong choice. In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.

%and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available in the network.

At a first cut, any time a router must make a decision locally between several route options, there is the possibility it might choose incorrectly. The PGIR captures this notion of choice precisely. For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the PGIR, possibly receiving announcements from $X$ or $Y$. However, regardless of whether $D$ chooses a route from $X$ or $Y$, the set of paths allowed by the policy after going through $D$ will be the same in either case. This remains true despite any failures that might have occurred in the network. Thus $D$ can safely prefer $X$ and $Y$ equally.

The more challenging case is when a topology location occurs in mutliple contexts in the PGIR. For example, in the compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an announcement from $E$ and later achieve the backup path, or it can receive an announcement from its neighbor $D$ and later achieve either the primary or backup path. Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$? The important observation is that, if $C$ prefers $D$, then it is never worse off---it will always achieve at least as good a path as if it had choosen $E$.
For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed. In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$. Since the $(C,3,2)$ node has the same one-step and two-step next hops as node $(C,-,2)$ in the product graph, no possible failure will prevent a route advertisment from reaching $(W,-,4)$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.

In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and enumerating all failures is intractable. We thus adopt a conservative analysis based on the observations above. The high-level idea is to order each PGIR node according to a \textit{can prefer} relation. For example, node $(C,3,2)$ can be preferred to node $(C,-,2)$, but not the other way around. Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures. Formally this means that $N_1$ can be preferred to $N_2$ when:
%
$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
%
where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
there is always a path to each ending location whenever this is a path from $N_2$ restricted to $G_i$.

@@

Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another. It walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step. 
When there is no equivalent step, the algorithm checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) that can protect against failures instead.
Thus any time $N_2$ can get to a final location for preference $i$, $N_1$ can get to at least the same final locations for a better preference $j$. The algorithm terminates since the number of related states $(x,y)$ that can be expolored is finite.

For each router in the topology, local preferences are now obtained by  sorting the corresponding PGIR nodes according to the \textit{can prefer} relation. If two nodes are incomparable, the compiler rejects the policy as unimplementable.

@@

\para{PG construction}

@@

\begin{figure}
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
  \caption{Configuration minimization. \label{fig:config-min}}
  \vspace{-1em}
\end{figure}

@@

@@

\subsection{Propane Properties}

\newtheorem{prop}{Proposition}[section]

%Here we investigate the correctness and expressiveness properties of \sysname. We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures? (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?

%If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario. We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges. We argue that \sysname is correct by breaking down the claim:

\begin{prop}
BGP configurations for internal routers produced by \sysname will be stable. 
\end{prop}

>>>>

\newcommand{\CD}[1]{\texttt{\small #1}}  % code font
\newcommand{\KW}[1]{\texttt{\small\bfseries{#1}}}
%\newcommand{\KW}[1]{\texttt{#1}}
\newcommand{\True}{\CD{true}}
\newcommand{\Define}{\KW{define}}
\newcommand{\Prefer}{\texttt{>>}}
\newcommand{\Path}{\texttt{=>}}
\newcommand{\Link}{\texttt{->}}
\newcommand{\Agg}{\KW{agg}}
\newcommand{\Any}{\KW{any}}
\newcommand{\None}{\KW{drop}}
\newcommand{\In}{\KW{in}}
\newcommand{\Out}{\KW{out}}
\newcommand{\AND}{\texttt{\&}}
\newcommand{\OR}{\texttt{|}}
\newcommand{\NOT}{\texttt{!}}
\newcommand{\Intersect}{\ensuremath{\cap}}
\newcommand{\Union}{\ensuremath{\cup}}

@@

Once \sysname compiles the policy, it is guaranteed to remain compliant under all possible failure scenarios, modulo any aggregation-induced black holes. In the presence of aggregation, the \sysname compiler will also efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.

@@

@@

  \caption{Regular Intermediate Language (RIL) syntax (left), and
           Propane language expansions (right).}
  \label{fig:rir-syntax}
  %\vspace{-1em}
\end{figure*}

@@

The first step in compilation is to reduce the \sysname front-end language (FE) to the simpler, regular intermediate representation (RIR) from Figure~\ref{fig:rir-syntax}.
The main differences between the FE and RIR are: $i)$ FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, $ii)$ FE provides high-level names that abstract sets of routes and groups of prefixes/neighbors, and $iii)$ FE allows the preference operator to be used more flexibly.

A key constraint when translating FE to RIR is to ensure that all specified routes are well-formed. In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$. This ensures that users only control traffic that goes through their network at some point, and that such traffic does not loop back multiple times through their network.

The translation from \sysname FE to RIR is based on a set of rewriting rules.
The first step merges separate constraints. It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by path negation ($\Any \cap \NOT(a)$). The additional constraint $\Any$ ensures the routes are well-formed by restricting the paths to only those that go through the user's network.
%
For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:

@@

The next step rewrites the high-level constraints such as \textit{enter} according to the equivalences in Figure~\ref{fig:rir-syntax}. Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression. For example, the regular expression $a \cdot (b \Prefer c) \cdot d$ is lifted to $(a \cdot b \cdot d) \Prefer (a \cdot c \cdot d)$ by distributing the preference over the sequence operator. In general, we employ the follwing distributivity equivalences:
%
\[ 
\begin{array}{c}
  x \odot (y_1 \Prefer \dots \Prefer y_n) = (x \odot y_1) \Prefer \dots \Prefer (x \odot y_n) \\
  (y_1 \Prefer \dots \Prefer y_n) \odot x = (y_1 \odot x) \Prefer \dots \Prefer (y_n \odot x)
\end{array}
\]
%
where $\odot$ stands for an arbitrary regular binary operator, and $x$ is a policy with a single preference. Preferences nested under a unary operator (i.e., \textit{star} or \textit{negation}) are flagged by the compiler as invalid policies.

@@

  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
  \label{fig:example-compilation}
  %\vspace{-1em}
\end{figure*}

Now that the user policy exists in a simplified form, we must consider the topology. In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints. Our PGIR captures these dependencies by ``intersecting" each of the regular automata corresponding to the RIR path preferences, and the topology. Paths through the PGIR correspond to real paths through the topology that satisfy the user constraints.

@@

% Formally define automata
The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$. While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., route announcements flowing in the opposite direction). To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression. Each automaton for the reversed regular expression of $r_i$ is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ consists of all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
% Formally define topology
The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon V \times V$.
%
% Formally define product graph
The combined PGIR is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon V' \times V'$,
a unique starting vertex $s$,
a unique ending vertex $e$,
and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
For a PGIR vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$, which indicates that the corresponding topology location for $v'$ is $v$. 
Two nodes $x$ and $y$ \emph{shadow} each other in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$.

@@

Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between routers.
%
Consider the topology in Figure~\ref{fig:example-compilation}. Suppose we want a primary route from neighbor W that allows traffic to enter the network at $A$, and utilize the C--D link before leaving the network (through $X$ or $Y$). As a backup, we also want to allow traffic to enter the network from $B$, in which case the traffic can also utilize the C--E link before leaving the network. For simplicity, we assume that the route ends in either $X$, $Y$, or $Z$. The RIR for the policy could be written as:
%
$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$$
%
Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
%
The figure also shows the PGIR after intersecting the topology and policy automata. Every path in the PGIR corresponds to a concrete path in the topology. In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
%
For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining a path with the most prefered preference of $1$.
BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This is reflected in the product graph by the node with state $(X,1,1)$. From here, if X were to advertise this route to D, it would result in the path $D \cdot X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
%
The ``--" state indicates the corresponding automaton can not accept the current path or any extension of it. Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates that this path has preference 1.

@@

Before checking if policies captured by the PGIR are safe, we minimize the PGIR to improve our safety analysis. 
The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops. In particular, BGP's loop prevention mechanism forces an AS to reject any route for which it is already in the AS path.
%
For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 1 policy, but which contains a loop.
%
It often improves the precision of the failure-safety analysis to eliminate cases that are not possible due to loops. 
%For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading from the start node to $y$. Similarly, a node $x$ post-dominates a node $y$ in the PGIR if $x$ appears on every path from $y$ to the end node.
We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where $x$, $x'$ and $y$, $y'$ refer to PGIR nodes that shadow each other:
\begin{itemize}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item Remove $x$ if it is not reachable from the start node
\item Remove $x$ if it can not reach the end node
\item Remove $x$ if it is (post-)dominated by some $x'$
\item Remove edge ($x$, $y$) if $y$ is post-dominated by some $x'$
\item Remove edge ($x$, $y$) if $x$ is dominated by some $y'$
\end{itemize}
%We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} can be removed since it is never on a simple path to the end node because it must always go through node $(W,-,4)$. That is, node $(W,-,4)$ post-dominates node $(W,1,1)$. We repeatly apply the above minimizations to the PGIR until no further minimization is possible.
Colored nodes and dashed edges in Figure~\ref{fig:example-compilation} are removed after minimization since they are irrelvant to the BGP decision process.
%
%Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.

@@

\subsection{Failure Analysis}

To implement path preferences in routing, BGP uses local preferences on a per-device basis. However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult. This task becomes even more challenging in the presence of failures since routers running BGP lack a global view of the network and thus cannot make dynamic routing decisions based on the which network elements are up or down.

\para{An illustrative example}

To demonstrate the difficulty of generating device-local preferences, consider the simple policy for the topology in Figure~\ref{fig:unimplementable}, which says to prefer the top path over the bottom path:
%
$(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G})  \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$.
%
How could such a policy be implemented in BGP? Suppose we set the local preferences to have $D$ prefer $E$ over $F$, and have $A$ prefer $B$ over $C$. This works as expected under normal conditions, however, if the B--D link fails, then suddenly $D$ has made the wrong decision by preferring $E$. Traffic will now follow the
$A \cdot C \cdot D \cdot E \cdot G$ path, even though this path was not allowed by the policy. This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy. To make matters worse, the second preference $A \cdot C \cdot D \cdot F \cdot G$ is available in the network but not being used. This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.

The soundness violation could be fixed by tagging and filtering route advertisements appropriately to have $C$ reject routes that went through $E$, however the completeness violation can not be fixed. In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures. The problem is that $D$ might "regret" its choice depending on what failures have occurred downstream.

\begin{figure}[t!]
  \centering
  \includegraphics[width=.8\columnwidth]{figures/unimplementable}
  \caption{Example topology for which the \sysname policy: $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
  \label{fig:unimplementable}
  %\vspace{-1em}
\end{figure}

\para{Problem Formulation}

The problem of deciding local preferences for each router is closely reflected in the structure of the PGIR. In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes), then the compiler must decide which context to prefer.
%
For example, in our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in context $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in context $(C,3,2)$. 
%
The compiler's task is to determine a \emph{total ordering} of contexts for each router in the topology, which reflects the relative preference of advertisements received in each context. For example, if the compiler determines that context $(C,3,2)$ is preferred to context $(C,-,2)$, written as $(C,3,2) < (C,-,2)$, then $C$ will prefer advertisements heard from $D$ over $E$.

\para{Regret-free Preferences}

How should the compiler determine a total ordering of PGIR contexts for each router in a way that is \emph{sound} and \emph{complete} under all possible failures? To this end, we introduce \emph{regret-free} preferences, a sufficient condition for correctness motivated by the observations from our previous example. Intuitively, preferences are \emph{regret-free} if, whevever some router $r$ prefers an advertisement $X$ over another $Y$, there is always some policy-compliant path to each final (advertisement) destination that is at least as good as any path if it had accepted $Y$ instead.

We now explain this property more formally in terms of the structure of the PGIR. We use the notation $path(s,d)$ to say that there exists a path in the PGIR from $s$ to $d$. 
%
Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $min ~ P(d'') \leq min ~ P(d')$.
%
The property simply states that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (higher ranked) path from $N_1$ to destination $d$. 
%
For example, the compilation example in Figure~\ref{fig:example-compilation}, a choice for $C$ to prefer context $(C,3,2)$ to $(C,-,2)$ would be regret-free, since there is always at least as good a path to destination $W$ regardless of failures.

\para{A Preference Inference Algorithm}

%For example, in our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an announcement from $E$ and later achieve the backup path, or it can receive an announcement from its neighbor $D$ and later achieve either the primary or backup path. Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$? The important observation is that, if $C$ prefers $D$, then it is never worse off---it will always achieve at least as good a path as if it had choosen $E$.
%For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed. In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$. Since the $(C,3,2)$ node has the same one-step and two-step next hops as node $(C,-,2)$ in the product graph, no possible failure will prevent a route advertisment from reaching $(W,-,4)$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.

Clearly searching for \emph{regret-free} preferences by enumerating all possible combinations of failures and preference orderings is intractable. We thus adopt a conservative analysis that we found to be highly-effective in practice. The idea is to search for regret-free preferences while also refining the search when possible by taking into account information about where advertisements must have already traversed.

The analysis determines that context $N_1 < N_2$ if the following condition holds:
%
$$\forall i, ~\exists j, ~j \leq i ~\wedge~ protect(G_j, N_1, G_i, N_2)$$
%
where \textit{protect} checks if, from $N_1$ in the product graph restricted to nodes that can potentially achieve a path with preference $j$ or better, there is always a path to each final location whenever there is a path from $N_2$ restricted to $G_i$ to the same final location.

@@

Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another. The algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step. 
%
When there is no equivalent step, the algorithm relaxes the regret-free property to take into account where the advertisement came from before reaching $N_1$. In particular, it checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) that can protect against failures instead.
Thus any time $N_2$ has a path to a final location for preference $i$, $N_1$ can get to at least the same final locations for a preference $j$, which is at least as good. The algorithm terminates since the number of related states $(x,y)$ that can be explored is finite.

For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(<)$ relation. If two nodes are incomparable, then the compiler rejects the policy as unimplementable.

@@

\para{PGIR construction}

@@

@@

\begin{figure}[t!]
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
  \caption{Configuration minimization. \label{fig:config-min}}
  \vspace{-1em}
\end{figure}

@@

%\subsection{Propane Properties}
%
%\newtheorem{prop}{Proposition}[section]
%
%Here we investigate the correctness and expressiveness properties of \sysname. We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures? (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
%
%If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario. We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges. We argue that \sysname is correct by breaking down the claim:
%
%\begin{prop}
%BGP configurations for internal routers produced by \sysname will be stable. 
%\end{prop}
%
%\begin{prop}
%BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
%\end{prop}
%
%The Soundness claim follows directly from compilation of the product graph. Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound. 
%
%\begin{prop}
%BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
%\end{prop}
%
%The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.  This means there is a valid path in the product graph corresponding to this path, and which is available in the network. 
%Assume we are unable to achieve this route in the network. To not achieve this path means that some router along the advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead. This implies that router that makes the ``wrong'' choice appears as a separate node in the product graph. However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node (from which it stole the route) for at least as good of a final preference. The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.
%
%Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
%
